A meta-analysis of the impacts of best management practices on nonpoint source pollutants.

### 2024-01-31 frontiers_submission/frontiers_submission.tex
finish regressions

@@

A source of uncertainty comes from the substantial variability of
performance metrics reported in empirical BMP studies
\citep{linternBestManagementPractices2020}. Previous empirical reviews
generally describe high variability and uncertainty in nitrogen and
phosphorus removal and consistent reduction in total suspended sediment
concentrations across BMP types
\citep{linternBestManagementPractices2020, liuReviewEffectivenessBest2017, kochNitrogenRemovalStormwater2014, claryBMPPerformanceAnalysis2011, barrettComparisonBMPPerformance2008, grudzinskiDoesRiparianFencing2020}.
The review literature on the effects of BMPs on FIBs are sparse but
generally find extremely high variance in performance across BMPs
\citep{claryBMPPerformanceAnalysis2011, grudzinskiDoesRiparianFencing2020}.
Accurately characterizing BMP treated runoff quality is challenging due
to the high variability in BMP performance. However, influent water
quality, seasonality, and BMP age provide some explanatation to highliy
heterogenous BMP efficiency data
\citep{barrettPerformanceComparisonStructural2005, liuReviewEffectivenessBest2017}.\\
A recent meta-analysis demonstrated the further linkages between local
climatic conditions and BMP performance on nitrogen and phosphorus
concentrations \citep{horvathEffectsRegionalClimate2023}.

@@

We conducted a systematic review of recent (2000-2022) literature to
compile field studies documenting the effectiveness of best management
practices on fecal indicator bacteria and nutrients concentrations. The
systematic review followed guidance provided in the Collaboration for
Environmental Evidence systematic review guidelines
\citep{collaborationforenvironmentalevidenceGuidelinesStandardsEvidence2018}.
In order to maximize the number of studies included in the review, we
included both peer-reviewed studies and unpublished white papers to
reduce potential bias against negative results. The inclusion criteria
filtered out (1) non-field studies, (2) modelling results, (3) studies
that did not evaluate specific BMPs, (4) studies conducted outside of
the U.S. or published in a language other than English. We ran search
queries in Texas A\&M Library Catalog, Web of Science, and Google
Scholar. Although results from Google Scholar are not always replicable,
we utilized the service to maximize search results for studies not
published in academic journals and presumably increase the chance of
identifying studies with negative effects. Fecal indicator bacteria
study seraches included the following query: ``fecal indicator
bacteria'' OR ``E. coli'' OR ``Escherichia coli'' OR ``enterococci'' OR
``enterococcus'' AND ``best management practices'' OR ``BMPs'' AND
``effectiveness'' OR ``performance''. Nutrient BMP studies utilized a
similar query: ``nutrient'' OR ``nitrogen'' OR ``phosphorus'' OR
``sediment'' OR ``TSS'' AND ``best management practices'' OR ``BMPs''
AND ``effectiveness'' OR ``performance''.

Results from each database were first filtered to remove duplicates.
After removal of duplicates, each member of the research team (\emph{n}
= 4) was assigned a subset of studies to evaluate if they should be
included. \textbf{include supplementary tables with inclusion criteria
and data variables} Each study was reviewed by two team members and
differences in opinion were collectively discussed and agreed upon
before progressing. The remaining studies were split among team members
for data extraction, again with at least two team members reviewing each
study. If data was provided in figures, the data was extracted with the
WebPlotDigitizer tool \citep{rohatgiWebPlotDigitizer2022}.

@@

\caption{\label{tab:datvars}Study and effect variables extracted for review.}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{10em}>{\raggedright\arraybackslash}p{25em}}
\toprule
Variable & Description\\
\midrule
Publication Year & Year the study was published\\
Parameter & The specific pollutant measured.\\
Runoff source & Dominant source of runoff (rop fields, livestock pasture, commerical, residential\\
Source type & Major categorization of runoff source: agricultural or urban\\
BMP & BMP evaluated\\
\addlinespace
BMP Classification & BMP description based on NRCS conservation practice standards and EPA BMP fact sheets\\
BMP Category & BMP categorization based on structural or management\\
BMP Subcategory & BMP subcategorization based on pollutant removal processes\\
Study scale & Spatial scale of the study area ("lot/field", "community", "watershed")\\
Location & Location name used in the study description\\
\addlinespace
State & State where the study was conducted\\
Study area & Drainage area in hectares\\
Longitude & Approximated or reported latitude coordinate\\
Latitude & Approximated or reported longitude coordinate\\
Study years & Year or years when data were collected\\
\addlinespace
N control & Number of control measurements\\
N experiment & Number of experiemental measurements\\
X control & Mean concentration for control measurements\\
X experiment & Mean concentration for experiemental measurements\\
SE control & Standard error of control measurements\\
\addlinespace
SE experiment & Standard error of experimental measurements\\
Minimum control & Minimum control measurement\\
Minimum experiment & Minimum experiment measurement\\
Maximum control & Maximum control measurement\\
Maximum experiment & Maximum experiment measurement\\
\addlinespace
SD control & Standard deviation of control measreuments\\
SD experiment & Standard deviation of experimental measurements\\
Units & Units reported by the study\\
Percent reduction & BMP efficiency for studies that only reported efficiency\\
\bottomrule
\end{tabular}
\end{table}

\hypertarget{effect-size-calculation}{%
\subsection*{Effect size calculation}\label{effect-size-calculation}}
\addcontentsline{toc}{subsection}{Effect size calculation}

Prior BMP reviews routinely report the effect of BMPs using efficiency
values
\citep[see][]{agouridisLivestockGrazingManagement2005, krogerReviewBestManagement2012, liuEnhancingRainfallrunoffModel2015, simpsonDevelopingBestManagement2009}.
Efficiency values are calculated as:

\[
\text{Efficiency}=\frac{x_{control}-x_{experiment}}{x_{control}}\times 100,
\]

where \emph{x\textsubscript{control}} is the pre-treatment or control
pollutant concentration and \emph{x\textsubscript{experiment}} is the
pollutant concentration measured after the BMP intervention. There are
several statistical shortcomings (distributional asymetry, skewness, and
non-additive properties) when using efficiency to estimate overall
effect sizes
\citep{nuzzoPercentDifferencesAnother2018, coleStatisticsNotesWhat2017}.
In comparision, the log ratio of means (\emph{ROM}) provide preferable
statistical properties for regression analysis
\citep{osenbergEffectSizeEcological1997, hedgesMetaanalysisResponseRatios1999}.
\emph{ROM} quantifies the difference in means between the control and
experimental group \citep{hedgesMetaanalysisResponseRatios1999}:

\[
ROM_i = ln\left(\frac{x_{i,control}}{x_{i,experiment}}\right) = ln(x_{i, control})-ln(x_{i, experiment}),
\] where \emph{x\textsubscript{i,control}} and
\emph{x\textsubscript{i,experiment}} are the mean pollutant
concentrations for experiment \emph{i}. The statistical properties of
\emph{lnRR} (normal distribution around zero and additive properties)
are preferable to the more commonly reported efficiency metric
\citep{osenbergEffectSizeEcological1997, hedgesMetaanalysisResponseRatios1999}.
Use of \emph{ROM} required the exclusion of studies that only provided
measures of BMP efficiency and not the underlying data used to derive
the metric.

@@

We used the ``rma.mv'' function in the \emph{metafor} R package to fit
multilevel random effects linear models with \emph{ROM} as the effect
variable
\citep{viechtbauerConductingMetaanalysesMetafor2010, rcoreteamLanguageEnvironmentStatistical2023}.
Our models specified a nested random effects term accounting for
heterogeneity between effect sizes from the same study and for
heterogeneity between studies. A key feature of meta-analysis is the
weighting of effects using sampling variance of individual effect sizes.
45\% of fecal indicator bacteria, 68\% of TN, 68\% of TP, and 70\% of
TSS effect sizes were missing standard deviations required to estimate
sampling variance. Removal of studies due to missing variance
information can introduce substantial bias
\citep{kambachConsequencesMultipleImputation2020}, so we imputed missing
standard deviations using random forest based multivariate imputation
with chained equations using the \emph{mice} R package
\citep{buurenMiceMultivariateImputation2011}. Sampling variance was
estimated with the variance estimator described in Doncaster et al.~to
reduce bias in small sample studies:

@@

Our initial models included log transformed pre-treatment pollutant
concentration, study scale (plot/field, community, watershed), study
length (\emph{n} years), BMP subcategory (), and pollutant
concentration:BMP subcategory interactions were included as fixed effect
terms. We used an information-theoretic approach to select the most
parsimonious model from the subset of candidate models based on
corrected Akaike information criterion (AIC\textsubscript{c}) estimated
with maximum likelihood \citep{cinarUsingInformationTheoretic2021}. The
final model was selected from candidate models, which included all
combination and subsets of the full model, by eliminating candidate
models until the \(\Delta\)\emph{AIC\textsubscript{c}} reached \(\leq\)
2 \citep{burnhamAICModelSelection2011}. We estimated regression
coefficients of the selected model using restricted maximum likelihood.
Relative heterogeneity between and within studies were calculated using
the \emph{I\textsuperscript{2}} metric described in
\citet{nakagawaMethodologicalIssuesAdvances2012}. Marginal
\emph{R\textsuperscript{2}} was used to describe the amount of variance
explained by fixed effects \citep{nakagawaGeneralSimpleMethod2013}.

We tested for evidence of publication bias, in the form of small study
effect, by using the extension of Egger's regression applied to the
multilevel model framework that included adjusted sampling error as a
moderator \citep{nakagawaQuantitativeEvidenceSynthesis2023}. We did not
identify evidence of publication bias in the surveyed studies for fecal
indicator bacteria (\emph{Z} = -1.17, \emph{p} = 0.25), total nitrogen,
total phosphorus, or total suspended solids; therefore, adjustments for
publication bias were not included in the final models. We conducted a
sensitivity analysis of the robustness of overall effect sizes to
individual studies using leave-one-out analysis
\citep{nakagawaQuantitativeEvidenceSynthesis2023}. Outlier studies
identified in the sensitivity analysis are highlighted in Table X and
were removed prior to fitting the final models.

@@

\hypertarget{regression-results}{%
\subsection{Regression results}\label{regression-results}}

Some evidence of a relationship between input concentrations and fecal
indicator bacteria reductions. No evidence strong evidence that the type
of BMP changed the overall relationship.

@@

\caption{Summary table of moderator effects for performance of BMPs on fecal indicator bacteria concentrations.}
\centering
\begin{tabular}[t]{lrlrrrl}
\toprule
Moderator & \makecell[r]{Estimate\\(\textit{lnRR})} & 95\% CI & SE & \textit{T}-statistic & df & \textit{p}-value\\
\midrule
Intercept & 0.21 & {}[-2.07,2.48] & 1.06 & 0.19 & 14 & 0.85\\
\addlinespace[0.3em]
\multicolumn{7}{l}{\textbf{BMP Subcategories}}\\
\hspace{1em}Filtration & -0.39 & {}[-6.42,5.63] & 2.81 & -0.14 & 14 & 0.89\\
\hspace{1em}Infiltration & -1.24 & {}[-3.50,1.01] & 1.13 & -1.10 & 64 & 0.28\\
\hspace{1em}Livestock & -1.18 & {}[-3.25,0.89] & 0.96 & -1.23 & 14 & 0.24\\
\hspace{1em}Treatment & -1.56 & {}[-2.63,-0.49] & 0.53 & -2.92 & 64 & \textless 0.01\\
log(Concentration) & 0.20 & {}[0.084,0.32] & 0.059 & 3.42 & 65 & \textless 0.01\\
\bottomrule
\multicolumn{7}{l}{\rule{0pt}{1em}$I^{2}_{\text{total}}$=21.48, $I^{2}_{\text{study}}$=0, $I^{2}_{\text{effect}}$=21.48; $R^{2}_{\text{marginal}}$=0.46}\\
\end{tabular}
\end{table}

\caption{Summary table of moderator effects for performance of BMPs on nitrogen removal.}
\centering
\begin{tabular}[t]{lrlrrrl}
\toprule
Moderator & \makecell[r]{Estimate\\(\textit{lnRR})} & 95\% CI & SE & \textit{T}-statistic & df & \textit{p}-value\\
\midrule
Intercept & 0.95 & {}[0.38,1.52] & 0.28 & 3.41 & 28 & \textless 0.01\\
log(Concentration) & -0.034 & {}[-0.14,0.071] & 0.053 & -0.64 & 124 & 0.525\\
Adjusted sampling error & -1.54 & {}[-3.30,0.22] & 0.89 & -1.74 & 124 & 0.085\\
\bottomrule
\multicolumn{7}{l}{\rule{0pt}{1em}$I^{2}_{\text{total}}$=96.57, $I^{2}_{\text{study}}$=52.45, $I^{2}_{\text{effect}}$=44.12; $R^{2}_{\text{marginal}}$=0.05}\\
\end{tabular}
\end{table}

\caption{Summary table of moderator effects for performance of BMPs on phosphorus removal.}
\centering
\begin{tabular}[t]{lrlrrrl}
\toprule
Moderator & \makecell[r]{Estimate\\(\textit{lnRR})} & 95\% CI & SE & \textit{T}-statistic & df & \textit{p}-value\\
\midrule
Intercept & 0.40 & {}[-0.14,0.93] & 0.26 & 1.52 & 28 & 0.14\\
log(Concentration) & 0.27 & {}[0.15,0.40] & 0.063 & 4.30 & 97 & \textless 0.01\\
\bottomrule
\multicolumn{7}{l}{\rule{0pt}{1em}$I^{2}_{\text{total}}$=15.54, $I^{2}_{\text{study}}$=0, $I^{2}_{\text{effect}}$=15.54; $R^{2}_{\text{marginal}}$=0.32}\\
\end{tabular}
\end{table}

\hypertarget{subsection-2}{%
\subsection{Subsection 2}\label{subsection-2}}

Frontiers requires figures to be submitted individually, in the same
order as they are referred to in the manuscript. Figures will then be
automatically embedded at the bottom of the submitted manuscript. Kindly
ensure that each table and figure is mentioned in the text and in
numerical order. Permission must be obtained for use of copyrighted
material from other sources (including the web). Please note that it is
compulsory to follow figure instructions. Figures which are not
according to the guidelines will cause substantial delay during the
production process.

>>>>

% From pandoc table feature
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}

@@

One source of uncertainty comes from the substantial variability of performance metrics reported in empirical BMP studies \citep{linternBestManagementPractices2020}.
There have been varied attempts at synthesizing estimates of BMP efficiency to provide resource managers with knowledge for improved decision-making \citep{agouridisLivestockGrazingManagement2005, barrettComparisonBMPPerformance2008, claryBMPPerformanceAnalysis2011, grudzinskiDoesRiparianFencing2020, horvathEffectsRegionalClimate2023, kochNitrogenRemovalStormwater2014, krogerReviewBestManagement2012, liuReviewEffectivenessBest2017, simpsonDevelopingBestManagement2009}.
These reviews generally describe high variability and uncertainty in nitrogen and phosphorus removal and consistent reduction in total suspended sediment concentrations across BMP types \citep{linternBestManagementPractices2020, liuReviewEffectivenessBest2017, kochNitrogenRemovalStormwater2014, claryBMPPerformanceAnalysis2011, barrettComparisonBMPPerformance2008, grudzinskiDoesRiparianFencing2020}.
The review literature on the effects of BMPs on FIBs are sparse but generally find extremely high variance in performance across BMPs \citep{claryBMPPerformanceAnalysis2011, grudzinskiDoesRiparianFencing2020}.
Accurately characterizing BMP treated runoff quality is challenging due to the high variability in BMP performance.
However, influent water quality, seasonality, and BMP age provide some explanation to highly heterogeneous BMP efficiency data \citep{barrettPerformanceComparisonStructural2005, liuReviewEffectivenessBest2017}.\\
A recent meta-analysis demonstrated the strong linkages between local climatic conditions and phosphorus removal in BMPs \citep{horvathEffectsRegionalClimate2023}.

\hypertarget{effect-size-calculations}{%
\subsection{Effect size calculations}\label{effect-size-calculations}}

Results from BMP studies are often reported as BMP efficiency (or percent reduction):

\[
\text{BMP}_{\text{eff}}=\frac{x_{control}-x_{experiment}}{x_{control}}\times 100,
\]

where \emph{x\textsubscript{control}} is the pre-treatment or control pollutant concentration and \emph{x\textsubscript{experiment}} is the pollutant concentration measured after the BMP intervention.
Several BMP data synthesis efforts have applied statistical summaries or regressions using BMP efficiency as the response variable of interest \citep{agouridisLivestockGrazingManagement2005, claryBMPPerformanceAnalysis2011, kochNitrogenRemovalStormwater2014, krogerReviewBestManagement2012, liuReviewEffectivenessBest2017, simpsonDevelopingBestManagement2009}.
There are several statistical shortcomings (distributional asymmetry, skewness, and non-additive properties) when using efficiency to estimate overall effect sizes across multiple studies that are cause for concern for metrics estimated using this approach \citep{nuzzoPercentDifferencesAnother2018, coleStatisticsNotesWhat2017}.
\citet{barrettPerformanceComparisonStructural2005} demonstrated the use of effluent concentration directly as a response variable improved the ability to describe BMP performance.
More recently, researchers have applied effect size calculations more commonly used in ecological meta-analysis.
\citet{horvathEffectsRegionalClimate2023} used the standardized mean difference between influent and effluent, calculated as the difference in the means divided by the pooled standard deviation of the two groups (\textbf{hedges}).
\citet{grudzinskiDoesRiparianFencing2020} applied the log ratio of means (\emph{ROM}) to summarize performance of livestock BMPs.
\emph{ROM} quantifies the difference in means between the control and experimental group \citep{hedgesMetaanalysisResponseRatios1999}:

\[
ROM_i = ln\left(\frac{x_{i,control}}{x_{i,experiment}}\right) = ln(x_{i, control})-ln(x_{i, experiment}),
\]

where \emph{x\textsubscript{i,control}} and \emph{x\textsubscript{i,experiment}} are the mean pollutant concentrations for experiment \emph{i}.
The statistical properties of \emph{ROM} (normal distribution around zero and additive properties) are preferable to using BMP efficiency \citep{osenbergEffectSizeEcological1997, hedgesMetaanalysisResponseRatios1999}.
\emph{ROM} \textgreater 0 indicates higher percent reductions and \emph{ROM} \textless indicates pollutant leaching.
One advantage of \emph{ROM} is that the statistical results calculated using \emph{ROM} are easily transformed to BMP efficiency for interpretation:

\[
\text{BMP}_{\text{eff}} = \left( 1 - \frac{1}{e^{ROM}}\right) \times 100
\]

The goals of this project were to (1) conduct a systematic review of BMP field studies; (2) develop estimates of FIB, nitrogen, phosphorus, and TSS removal using a meta-analytic approach; and (3) explore the effect of multiple moderators using multilevel random effects meta-analytic regression models.

@@

We conducted a systematic review of recent (2000-2022) literature to compile field studies documenting the effectiveness of best management practices on fecal indicator bacteria and nutrients concentrations.
Prior meta-analysis have utilized data reported in the International Stormwater Database, which consists of self-reported and quality checked BMP data \citep{claryBMPPerformanceAnalysis2011, kochNitrogenRemovalStormwater2014, horvathEffectsRegionalClimate2023}.
The International Stormwater Database only recently added agricultural BMPs and has relatively sparse FIB data \citep{claryBMPPerformanceAnalysis2011, kochNitrogenRemovalStormwater2014}.
Since we had interest in both FIB performance and agricultural BMPs we chose to utilize a systematic review.
We also assume that most published reports undergo some method of internal or external peer review prior to publication, which is not necessarily the case with all of the data published in the International Stormwater Database.

The systematic review followed guidance provided in the Collaboration for Environmental Evidence systematic review guidelines \citep{collaborationforenvironmentalevidenceGuidelinesStandardsEvidence2018}.
In order to maximize the number of studies included in the review, we included both peer-reviewed studies and unpublished white papers to reduce potential bias against negative results.
The inclusion criteria filtered out (1) non-field studies, (2) modelling results, (3) studies that did not evaluate specific BMPs, (4) studies conducted outside of the U.S. or published in a language other than English.
We ran search queries in Texas A\&M Library Catalog, Web of Science, and Google Scholar.
Although results from Google Scholar are not always replicable, we utilized the service to maximize search results for studies not published in academic journals and presumably increase the chance of identifying studies with negative effects.
Fecal indicator bacteria study seraches included the following query: ``fecal indicator bacteria'' OR ``\emph{E. coli}'' OR ``\emph{Escherichia coli}'' OR ``enterococci'' OR ``enterococcus'' AND ``best management practices'' OR ``BMPs'' AND ``effectiveness'' OR ``performance''. Nutrient BMP studies utilized a similar query: ``nutrient'' OR ``nitrogen'' OR ``phosphorus'' OR ``sediment'' OR ``TSS'' AND ``best management practices'' OR ``BMPs'' AND ``effectiveness'' OR ``performance''.

Results from each database were first filtered to remove duplicates.
After removal of duplicates, each member of the research team (\emph{n} = 4) was assigned a subset of studies to evaluate if they should be included (Table \ref{tab:criteria}).
Each study was reviewed by two team members and differences in opinion were collectively discussed and agreed upon before progressing.
The remaining studies were split among team members for data extraction (Table \ref{tab:datvars}), again with at least two team members reviewing each study.
If data was provided in figures, the data was extracted with the WebPlotDigitizer tool \citep{rohatgiWebPlotDigitizer2022}.

@@

\caption{\label{tab:datvars}Study and effect variables extracted for review.}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{10em}>{\raggedright\arraybackslash}p{25em}}
\toprule
Variable & Description\\
\midrule
Publication Year & Year the study was published\\
Parameter & The specific pollutant measured.\\
Runoff source & Dominant source of runoff (crop fields, livestock pasture, commerical, residential\\
Source type & Major categorization of runoff source: agricultural or urban\\
BMP & BMP evaluated\\
\addlinespace
BMP Classification & BMP description based on NRCS conservation practice standards and EPA BMP fact sheets\\
BMP Category & BMP categorization based on structural or management\\
BMP Subcategory & BMP subcategorization based on pollutant removal processes\\
Study scale & Spatial scale of the study area ("lot/field", "community", "watershed")\\
Location & Location name used in the study description\\
\addlinespace
State & State where the study was conducted\\
Study area & Drainage area in hectares\\
Longitude & Approximated or reported latitude coordinate\\
Latitude & Approximated or reported longitude coordinate\\
Study years & Year or years when data were collected\\
\addlinespace
N control & Number of control measurements\\
N experiment & Number of experiemental measurements\\
X control & Mean concentration for control measurements\\
X experiment & Mean concentration for experiemental measurements\\
SE control & Standard error of control measurements\\
\addlinespace
SE experiment & Standard error of experimental measurements\\
Minimum control & Minimum control measurement\\
Minimum experiment & Minimum experiment measurement\\
Maximum control & Maximum control measurement\\
Maximum experiment & Maximum experiment measurement\\
\addlinespace
SD control & Standard deviation of control measreuments\\
SD experiment & Standard deviation of experimental measurements\\
Units & Units reported by the study\\
Percent reduction & BMP efficiency for studies that only reported efficiency\\
\bottomrule
\end{tabular}
\end{table}

@@

We used the ``rma.mv'' function in the \emph{metafor} R package to fit multilevel random effects regression models with \emph{ROM} as the effect variable \citep{viechtbauerConductingMetaanalysesMetafor2010, rcoreteamLanguageEnvironmentStatistical2023}.
Our models specified a nested random effects term accounting for heterogeneity between effect sizes from the same study and for heterogeneity between studies.
\emph{ROM} was used as the effect size which required the exclusion of studies that only provided measures of BMP efficiency and not the underlying data used to derive the metric.
A key feature of meta-analysis is the weighting of effects using sampling variance of individual effect sizes.
Fifty-nine percent of 222 effect sizes were missing standard deviations required to estimate sampling variance.
Removal of studies due to missing variance information can introduce substantial bias \citep{kambachConsequencesMultipleImputation2020}.
Missing standard deviations were imputed using the pooled ratio of the mean effect size to coefficient of variation (CV) \citep{brackenStatisticalMethodsAnalysis1992}.
Sampling variance was estimated utilizing the average squared CV across all studies divided by sample size for each effect \citep{nakagawaRobustReadilyImplementable2023, doncasterCorrectionBiasMeta2018}:

@@

Our initial models included log transformed influent concentration, BMP subcategory (drainage modification, crop field management, livestock management, filtration, treatment, detention, or infiltration), aridity index (mean-centered), influent concentration\texttimes BMP subcategory interactions, and aridity index\texttimes BMP subcategory interactions were included as fixed effect terms.
Aridity index was the only moderator not obtained directly in the systematic review (Table \ref{tab:datvars}).
We mapped study location coordinates to aridity index values published in the ``Global Aridity Index and Potential Evapotranspiration Database - Version 3'' (Global-AI\_PET\_v3) which provides gridded 30 arc-second annual average precipitation and potential evapotranspiration estimates \citep{zomerVersionGlobalAridity2022}.
The aridity index is calculated as the ratio of mean annual precipitation to mean annual evapotraspiration with values between 0 and 0.5 considered hyper to semi-arid, and values above 0.65 as humid.

We used an information-theoretic approach to select the most parsimonious model from the subset of candidate models based on corrected Akaike information criterion (AIC\textsubscript{c}) estimated with maximum likelihood \citep{cinarUsingInformationTheoretic2021}.
Candidate models used for variable selection were fit with maximum likelihood (ML).
The final model was selected from candidate models, which included all combination and subsets of the full model, by selecting the model with the lowest AIC\textsubscript{c} score \citep{burnhamAICModelSelection2011, cinarUsingInformationTheoretic2021}.
Regression coefficients of the selected model were estimated using restricted maximum likelihood (REML).
Relative heterogeneity between and within studies were calculated using the \emph{I\textsuperscript{2}} metric described in \citet{nakagawaMethodologicalIssuesAdvances2012}.
Marginal \emph{R\textsuperscript{2}} was used to describe the amount of variance explained by fixed effects \citep{nakagawaGeneralSimpleMethod2013}.

We tested for evidence of publication bias, in the form of small study effect, by using the extension of Egger's regression applied to the multilevel model framework that included adjusted sampling error as a moderator \citep{nakagawaQuantitativeEvidenceSynthesis2023}.
We did not identify evidence of publication bias in the surveyed studies (FIB: ROM = 1.19, 95\% CI {[}-3.23, 5.61{]}; TN: ROM = 0.31, 95\% CI {[}-1.15, 1.78{]}; DIN: ROM = -2.4, 95\% CI {[}-6.14, 1.59{]}; TP: ROM = -1.97, 95\% CI {[}-5.18, 1.23{]}; PO\textsubscript{4}: -0.05, 95\% CI {[}-2.82, 2.72{]}; TSS: ROM: 0.31, 95\% CI {[}-1.15, 1.78{]}; Figure S1-S6); therefore, adjustments for publication bias were not included in the final models.
We conducted a sensitivity analysis of the robustness of overall effect sizes to individual studies using leave-one-out analysis \citep{nakagawaQuantitativeEvidenceSynthesis2023}.
This approach repeatedly fits the selected model leaving out an individual value each time.
The overall effect and 95\% CI from each refit model is compared to the overall effect and 95\% CI of the model fit to the full dataset.
We did not identify evidence of outliers or overly influential studies for any of our models (Figure S7-S12).

@@

There were a total of 33 studies and 125 effect sizes on FIB, 24 studies and 50 effect sizes on TN, 31 studies and 88 effect sizes for DIN, 31 studies and 61 effect sizes for TP, 17 studies and 36 effects for PO\textsubscript{4}, and 33 studies with 125 effect sizes for TSS.
The majority of studies were identified as smaller scaled lot or field studies (Figure \ref{fig:bmpsummary} A).
FIB studies had a roughly equal proportion large watershed/catchment studies and studies conducted at the commuity/farm scale or smaller.
We also identified that the majority of studies (all parameters) were conducted on urban or non-agricultural runoff (Figure \ref{fig:bmpsummary} B).
We did identify a wide variety of BMPs in the review, but it did not appear that any particular type of BMP was responsible for the majority of studies for any given parameter (Figure \ref{fig:bmpsummary} C).
Our review was resticted to studies published after 1999.
The number of studies published for each parameter were roughly uniformly distributed over time (Figure \ref{fig:bmptemporal} A) and are not indicative of increases or decreases in the number of published studies.
Study length was strongly skewed for all parameters (Figure \ref{fig:bmptemporal} B). Median study lengths were 3 (DIN), 2 (FIB), 2.5 (PO\textasciitilde4), 2.5 (TN), 2.5 (TP), and 2 (TSS).
There appears to be a strong clustering of BMP studies in the mid-Atlantic region (North Carolina, Virginia, Maryland) with other states sparsely represented or completely absent from the review (Figure \ref{fig:studymap}).
This might suggest that spatially correlated predictors such as climate and soil variables would be difficult to model due to the poor spatial representation of the collected data.

\hypertarget{regression-models}{%
\subsection{Regression models}\label{regression-models}}

@@

\caption{\label{tab:modelaic}Model selection AICc}
\centering
\begin{tabular}[t]{lllllll}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{6}{c}{AICc} \\
\cmidrule(l{3pt}r{3pt}){2-7}
Candidate Models & FIB & TN & DIN & TP & PO\textsubscript4 & TSS\\
\midrule
$\sim$ Int & 208.9 & \textbf{37.7} & \textbf{112.6} & 96.7 & 42.1 & \textbf{103.9}\\
$\sim$ Int+Influent & 197.4 & 39.8 & 114.6 & \textbf{96.3} & \textbf{36.8} & 106.4\\
$\sim$ Int+AI & 209 & 40.3 & 114.8 & 98.2 & 45.2 & 106.5\\
$\sim$ Int+AI+Influent & 195 & 42.5 & 116.9 & 98.9 & 40.2 & 109.4\\
$\sim$ Int+BMP & 209.1 & 47.3 & 121 & 101.8 & 51.8 & 115.3\\
\addlinespace
$\sim$ Int+BMP+Influent & 196.7 & 48.9 & 124 & 102.3 & 45.6 & 120.4\\
$\sim$ Int+AI+BMP & 210.1 & 50.8 & 124.1 & 104.8 & 56.4 & 120.7\\
$\sim$ Int+AI+BMP+Influent & 195.6 & 52.9 & 127.3 & 105.6 & 50.8 & 126.6\\
$\sim$ Int+BMP\texttimes Influent & 201.3 & 67.5 & 133.7 & 121.5 & 62.9 & 174.1\\
$\sim$ Int+AI\texttimes BMP & 208.1 & 75.1 & 137.6 & 121 & 67.7 & 175.5\\
\addlinespace
$\sim$ Int+Influent+AI\texttimes BMP & \textbf{193.7} & 77.2 & 141.4 & 121.6 & 70.7 & 191.4\\
$\sim$ Int+AI+BMP\texttimes Influent & 202 & 83.2 & 145.9 & 127.3 & 72.9 & 191.9\\
$\sim$ Int+AI\texttimes BMP+BMP\texttimes Influent & 201.9 & 116.8 & 156.2 & 142.7 & 94.8 & 188.5\\
\bottomrule
\multicolumn{7}{l}{\rule{0pt}{1em}Int = intercept; AI = ariditiy index; BMP = BMP subcategory}\\
\end{tabular}
\end{table}

\hypertarget{fecal-indicator-bacteria}{%
\subsubsection{Fecal Indicator Bacteria}\label{fecal-indicator-bacteria}}

There were only 19 studies and 63 FIB effect sizes available to model after removal of studies and effects that only reported BMP\textsubscript{eff}.
The overall mean effect (estimated with the intercept only multilevel random effects model) showed significant mean reductions in FIB (ROM = 0.85, 95\% CI {[}0.36, 1.34{]}; BMP\textsubscript{eff} = 57.4\%, 95\% CI {[}30.4\%, 73.9\%{]}; Figure \ref{fig:overalleffect}) resulting from BMPs.
Total heterogeneity was moderate with a relatively large amount of heterogeneity observed due to differences within studies (\textit{I\textsuperscript{2}\textsubscript{total}} = 53.54, \textit{I\textsuperscript{2}\textsubscript{study}} = 10.03, \textit{I\textsuperscript{2}\textsubscript{effect}} = 43.51).

AICc scores included log transformed influent concentration and the aridity index\texttimes BMP subcategory interaction as moderators for the FIB model (Table \ref{tab:modelaic}).
Moderator terms and interactions explained a high proportion of effect size variance (\textit{R\textsuperscript{2}\textsubscript{marginal}} =0.89) in the FIB model.
Increased influent concentrations (\(\beta\) = 0.25, 95\% CI {[}0.14, 0.37{]}) resulted in significantly larger ROM effect for FIB (Figure \ref{fig:fibeffect}.
Compared to the baseline aridity index\texttimes detention BMP subcategory interaction, infiltration (\(\beta\) = -29.90, 95\% CI {[}-50.34, -9.47{]}), livestock management (\(\beta\) = -30.37, 95\% CI {[}-50.93, -9.81{]}), and treatment (\(\beta\) = -30.33, 95\% CI {[}-49.62, -11.03{]}) interactions had significantly smaller slopes.
However, the data had uneven coverage of BMP subcategories across the aridity index.
Effects for detention BMPs were clustered in humid climates (aridity index \textgreater{} 0.65) and the resulting estimate for the baseline interaction (\(\beta\) = 32.63, 95\% CI {[}12.57, 52.69{]}) may not be reliable.

\hypertarget{nitrogen}{%
\subsubsection{Nitrogen}\label{nitrogen}}

We identified 13 eligible TN studies and 14 DIN studies and 31 and 44 effect sizes respectively that could be included in the regression model.
Overall effects showed that BMPs resulted in significant mean reductions in TN (ROM = 0.42, 95\% CI {[}0.21, 0.62{]}; BMP\textsubscript{eff} = 34.0\%, 95\% CI {[}18.7\%, 46.4\%{]}; Figure \ref{fig:overalleffect}) but not in DIN (ROM = 0.64, 95\% CI {[}-0.08, 1.35{]}; BMP\textsubscript{eff} = 47.1\%, 95\% CI {[}-8.1\%, 74.1\%{]}; Figure \ref{fig:overalleffect}).
Heterogeneity was high for TN with a large proportion of heterogeneity attributed to within study effect (\textit{I\textsuperscript{2}\textsubscript{total}} = 77.12, \textit{I\textsuperscript{2}\textsubscript{study}} = 23.2, \textit{I\textsuperscript{2}\textsubscript{effect}} = 53.92).
The DIN model had even higher heterogeneity with a larger proportion attributed between studies (\textit{I\textsuperscript{2}\textsubscript{total}} = 99.51, \textit{I\textsuperscript{2}\textsubscript{study}} = 83.53, \textit{I\textsuperscript{2}\textsubscript{effect}} = 15.97).
AICc scores indicated that none of the moderators resulted in substantial improvement over the intercept only model (Table \ref{tab:modelaic}).

\hypertarget{phosphorus}{%
\subsubsection{Phosphorus}\label{phosphorus}}
